---
title: "Project" 
output:
  html_document:
    theme: cosmo
    highlight: monochrome
    toc: yes
    toc_float: yes
    toc_depth: 3
    code_folding: hide
---


Load packages
```{r echo = F, message=FALSE, warning=FALSE}
library ("rio")
library ("skimr")
library ("psych")
library ("tidyverse")
library ("car")
library("readxl")
library('psych')
library('rio')
library('tidyverse')
library('skimr')
library('psych')
library('dplyr')
library('car')
library('MASS')
library('QuantPsyc')
library('apaTables')
library ('Publish')
library('stargazer')
library('ggeffects') 
library('margins') 
library ('Publish')
library('stargazer')
library('plotROC') 
library('ggplot2')
library("plotROC")
```

#import data
```{r echo = F, message=FALSE, warning=FALSE}
data <- read_excel("C:/Users/alexs/df_satisfaction.xlsx", col_names = TRUE)
View(data)
```


```{r echo = F, message=FALSE, warning=FALSE}
attributes(data)
summary (data)
view (data)
describe (data)
skim(data)
```

#Statistics $where_learn
```{r echo = F, message=FALSE, warning=FALSE}
attributes(data$where_learn)
summary (data$where_learn)
view (data$where_learn)
describe (data$where_learn)
skim(data$where_learn)
hist.default(data$KF7, border = "dark orange", col = "dark orange",
             main = "Утверждение: Где вы изучали русский язык?", xlab = "Ответные категории", ylab = "Количество ответов")
```

#Statistics $tech_bags
```{r echo = F, message=FALSE, warning=FALSE}
attributes(data$tech_bags)
summary (data$tech_bags)
view (data$tech_bags)
describe (data$tech_bags)
skim(data$tech_bags)
hist.default(data$KF7, border = "dark green", col = "dark green",
             main = "Утверждение: Оцените технические проблемы", xlab = "Ответные категории", ylab = "Количество ответов")
```

#Statistics $KF7
```{r echo = F, message=FALSE, warning=FALSE}
attributes(data$KF7)
summary (data$KF7)
view (data$tech_bags)
describe (data$KF7)
skim(data$KF7)
hist.default(data$KF7, border = " dark blue", col = "dark blue",
             main = "Утверждение: Я замечал свой прогресс на каждом занятии этого курса", xlab = "Ответные категории", ylab = "Количество ответов")
```

#New dichotomic variable (course score)
```{r echo = F, message=FALSE, warning=FALSE}
data$score_dih <- recode(data$course_score, "8:10= 1; 0:8=0", as.numeric = TRUE)
summary(data$score_dih)
table(data$score_dih)
```

#Regression (pair)
```{r echo = F, message=FALSE, warning=FALSE}
Linear11<- lm(data$tech_bags ~ data$course_score, data=data)
print(Linear11)
summary(Linear11)
```

#### Binary regressin ####
# Firstly make a regression for each independent variable for binary variable (course score) 
```{r echo = F, message=FALSE, warning=FALSE}
model1 <- glm(formula = score_dih  ~tech_bags, data = data)
summary(model1)
exp(coef(model1))

model2 <- glm(formula = score_dih ~ where_learn, data = data)
summary(model2)
exp(coef(model2))

model3 <- glm(formula = score_dih ~ KF7, data = data)
summary(model3)
exp(coef(model3))

```

# Make a model wich all variable 
```{r echo = F, message=FALSE, warning=FALSE}

model4 <- glm(formula = score_dih ~ tech_bags + where_learn + KF7, data = data)
summary(model4)
exp(coef(model4))
```

# Visualise coefficient  - use packege ggeffects
# terms - independent variable for this plot
```{r echo = F, message=FALSE, warning=FALSE}
plot(ggpredict(model4, terms = "score_dih")) 
plot(ggpredict(model4, terms = c("score_dih", "where_learn")))
```

#Marginal effects (use package "margins") 
```{r echo = F, message=FALSE, warning=FALSE}
marg_fit <- margins(model4)
summary(marg_fit) 
plot(marg_fit, labels = c("Я замечал свой прогресс на каждом 
                          занятии этого курса.",
                          "Оцените технические проблемы",
                          "Где вы изучали русский язык?"
                          ))
```

# Х variables and У means 
# Make a ROC curve
```{r echo = F, message=FALSE, warning=FALSE}
data$pred  <- predict(object = model4, type = "response", newdata = data)
summary(data$pred)
```

# Use package "plotROC" get predict, argument d - observed variable, m -predictable variable 
```{r echo = F, message=FALSE, warning=FALSE}
ggplot(data, aes(d = score_dih, m= pred)) +
  geom_roc(labels = F)
ROC<-ggplot(data, aes(d = score_dih, m= pred)) +
  geom_roc(labels = F)
```

# Calculate curve
```{r echo = F, message=FALSE, warning=FALSE}
calc_auc(ROC)

```
#We have a 0,75 it means 75/25 our model with goof predictable features

#Plus Use stargazer packege to load our output in html file
```{r echo = F, message=FALSE, warning=FALSE}
stargazer(model1, model2, model3, model4,
          type='html',   out='bin_regr_results1.html', 
          apply.coef = exp,  t.auto=F )
```

# Plus Add title and labels for table
```{r echo = F, message=FALSE, warning=FALSE}
stargazer(model1, model2, model3, model4,
          dep.var.labels="Оценка курса",
          covariate.labels=c("Оцените технические проблемы",
                             "Где вы изучали русский язык?",
                             "Я замечал свой прогресс на каждом занятии этого курса."),
          type='html',   out='bin_regr_results.html', 
          apply.coef = exp,  t.auto=F)
```


```
